Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Resolve comment on PDP results
@ConnectedSystems I agree with your comment. I must not have updated that sentence since last rf figure revision. I've resolved it now.

Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics suggest
that reefs with greater outgoing connectivity and lower incoming connectivity levels have
higher probability of being clustered into the Low cover cluster compared to other reefs
**\[Ben, I disagree with this assessment and the next sentence seems to contradict it?\]**.
Additionally, two-way analyses revealed little interaction between depth and incoming and
outgoing connectivity metrics for reef clustering probabilities
(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
median depth around 15m and high incoming connectivity may benefit slightly, with higher
probability of High cover cluster assignment compared to 15m - depth reefs with lower
connectivity.

>>>>

First-order partial dependence analysis showed minimal influence of incoming, outgoing and
source-to-sink ratio connectivity metrics on cluster assignment probabilities. Two-way
analyses revealed little interaction between depth and incoming and outgoing connectivity
metrics for reef clustering probabilities (@fig-ts-cluster-pdp-twoway-incoming;
@sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a median depth around 15m and high
incoming connectivity may benefit slightly, with higher probability of High cover cluster
assignment compared to 15m - depth reefs with lower connectivity.
